Viscous Transport in Eroding Porous Media

### 2019-08-08 docs/transport/erosion_transport.tex
small changes
small changes in results

There have been efforts to relate the tortuosity to the
porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
al.~\cite{matyka2008tortuosity} propose the models
\begin{align}
  T(\phi) &= \phi^{-p}, \\
  T(\phi) &= 1-p \log \phi, \\
  T(\phi) &= 1+p (1-\phi), \\
  T(\phi) &= (1+p (1-\phi))^2, 
\end{align}
where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
compare these four models with the tortuosity of eroding geometries.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
\todo[inline]{S-H: Can cut the ylimit at 1.3}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
averaged tortuosity through the channel is $1.098$.  (c) The
trajectories resulting in the ten largest differences between
neighboring trajectories.  Neighboring trajectories have the same
color.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.2064$ and 
the root mean square deviation is $5.9 \times 10^{-3}$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort1}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort150}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort300}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort450}
\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. }
\end{center}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian20b}
\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots).
The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.1669$ and 
the root mean square deviation is $1.13 \times 10^{-2}$.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity. 
The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
the root mean square deviation is $5.2 \times 10^{-3}$.}
\end{figure}

>>>>

There have been efforts to relate the tortuosity to the
porosity~\cite{matyka2008tortuosity}.  For example, Matyka et
al.~\cite{matyka2008tortuosity} propose the models
\begin{subequations}
  \label{eqn:tortuosityModels}
  \begin{align}
    \widehat{T}(\phi) &= \phi^{-p}, \\
    \widehat{T}(\phi) &= 1-p \log \phi, \\
    \widehat{T}(\phi) &= 1+p (1-\phi), \\
    \widehat{T}(\phi) &= (1+p (1-\phi))^2, 
  \end{align}
\end{subequations}
where $p>0$ is a fitting parameter.  In Section~\ref{sec:results}, we
compare these four models with the tortuosity of eroding geometries.

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =0.97\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_diff_top10_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of an eroded geometry
with porosity 62.9\%. (a) The x-component of the velocity $u(-1, y)$
normalized by its maximum velocity of $2.98 \times 10^{-3}$. (b) The
local tortuosity $\tau(y)$ on the cross section $x = -1$.  The spatially
averaged tortuosity through the channel is $1.098$.  (c) The
trajectories resulting in the ten largest differences between
neighboring trajectories.  Neighboring trajectories have the same
color.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$ as
$p=0.2064$ and the root-mean-square error is $5.9 \times 10^{-3}$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is ???\todo[inline]{SH: Fill in this number}.  At this
resolution, this corresponds to a spacing of ???$h$ which is much
too small for the trapezoid rule.  By applying the Barycentric
quadrature rule, there is no issue simulating the erosion until all the
bodies have eroded.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort1}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort150}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort300}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort450}
\end{center}
\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching
bodies with the fixed pressure drop condition. The color is the
vorticity of the fluid. The 4 snapshots are evenly spaced in time. We
use $N_\iin = 256$ discretization points on the body, a time-step of
$\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
$\sigma=10/256 $. }
\end{figure}

We compute the tortuosity using the Eulerian
method~\eqref{eqn:tortuosity2}. In Figure~\ref{fig:ErodingLow20tort}, we
plot the tortuosity with respect to the porosity (blue) and a line of
best fit (black) using the power law $\widehat{T}(\phi) =
\phi^{-p}$~\cite{matyka2008tortuosity}.  This model outperformed the
other three models described in equation~\eqref{eqn:tortuosityModels}.
The root-mean-squared error of the power law is $1.13 \times 10^{-2}$.

Unlike the previous 20 body simulation, the tortuosity decreases
monotonically with the porosity. \todo[inline]{BQ: Why is this the case?
What is special about the last example?}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian20b}
\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
as $p=0.1669$ and the root mean square deviation is $1.13 \times
10^{-2}$.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
approach of tortuosity.  The blue dots are Eulerian approach of
tortuosity and the red stars and square are Lagrangian approach of
tortuosity.  The dash line is the fitting line
$\widehat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and the root mean square
deviation is $5.2 \times 10^{-3}$.}
\end{figure}
